### 2024-02-21 docs/manuscript/manuscript.qmd
update on manuscript, tables and analysis
- descriptive tables
- mediation analysis on statistical analyses

**Título**: La Aptitud Física se Relaciona con la Grasa Corporal y la Respuesta Autonómica Cardíaca al Ejercicio Físico en Personas Mayores

**Title**: Physical Fitness is Related to Body Fat and Cardiac Autonomic Response to Exercise in Older People

**Autores**: Autor,^1^ Autor,^2^ Autor,^3^ Autor,^4^ Autor,^5^ Autor.^6^ \*

@@

### \*Autor de correspondencia

@@

<!---- Antecedentes históricos ---->

@@

<!---- Conceptualización del problema ---->

@@

<!---- Hipótesis y objetivos ---->

@@

### Short Physical Performance Battery

@@

### Body Composition

@@

### Cardiac Autonomic Activity

@@

### Two-Minutes Step Test

The TMST is a sub-test from the Senior Fitness Test, demanding a low to moderate intensity [@Rikli1999], [@ijerph20054456]. The test consists of a two-minute assessment designed to evaluate cardiorrespiratory fitness. Participants are instructed to raise their right knee to a marked point on a wall as many times as possible within the given time frame, ensuring that each raise reaches at least a 70° angle at the thigh-femoral joint.

@@

[...], using the *R* programming language for statistical computing, [@rlanguage].

@@

Sociodemographic characteristic of the sample can be seen in table 1.

>>>>

**Title**: Physical fitness is related to body fat and cardiac autonomic response to exercise in older people.

**Authors**: Autor,^1^ Autor,^2^ Autor,^3^ Autor,^4^ Autor,^5^ Autor.^6^ \*

@@

### \*Correspondence

@@

<!---- Historical precedents ---->

@@

<!---- Conceptualization of the issue ---->

@@

<!---- Hypothesis and main objectives ---->

@@

### Short physical performance battery

@@

### Body composition

@@

### Cardiac autonomic activity

@@

### Two-minutes step test

The TMST is a sub-test from the Senior Fitness Test, demanding a low to moderate intensity [@Rikli1999; @ijerph20054456]. The test consists of a two-minute assessment designed to evaluate cardiorrespiratory fitness. Participants are instructed to raise their right knee to a marked point on a wall as many times as possible within the given time frame, ensuring that each raise reaches at least a 70° angle at the thigh-femoral joint.

@@

We used mean and standard deviation (SD) to describe continuous variables, absolute and relative frequencies to describe discrete variables. In order to assess the realtionship between variables, we used Pearson's product-moment correlation (r), and to assess differences between groups we used standardized mean difference (SMD) and 95% confidence intervals (CI~95%~).

As a way of controlling for the influence of psycho-physiological variables on the cardiac autonomic response of the subjects to exercise, we assess the average causal mediaton effect (ACME), the average direct effect (ADE) of the main effects after taking into account the effect of moderator variables into the observed relationships and the proportion of the effect that its mediated by these variables. To assess the significance of moderating variables, we used non parametric bootstrapping by using Monte Carlo draws, and bias-corrected and accelerated CI~95%~.

We defined a type I error rate at 5% ($\alpha$ = 0.05) as our threshold for null hypothesis significance testing. All analyses were computed using the *R* programming language for statistical computing, [@rlanguage].

@@

The sample assessed consisted on 81 adults (age: 71.1 ± 6.2 years old,  BMI: 31 ± 6.2 kg/m^2^), of whom 67 (82.7%) were females. Sociodemographic and anthropometric characteristics of the sample can be seen in table 1.

```{r}
#| echo: false
#| message: false
#| warning: false
library(flextable)
readRDS(file = "tables/tbl-descriptives.RDS") |> 
  font(part = "all", fontname = "Times")
```
